Bridging the Gap Between Visual and Analytical Machine Learning Testing

### 2023-10-25 report/icst24.tex
improve Implications, conclusion and future work

Results for RQ1 indicate that combining ML visualisations with analytical assertions is an emerging testing practice within the ML community. However in results from RQ2, we see several examples of assertions that fail to capture all the information gained from its visual counter-part. Our observations indicate a need to bridge the gap between qualitative assessment of ML systems using visualisations and deriving analytical assertions from the visualisations. We find the need for automated tools that make this translation process easier for AI practitioners.

>>>>

The results for RQ1 indicate that the combination of machine learning visualizations with analytical assertions is an emerging testing practice within the machine learning community. We found only 54,000 notebooks that contain the keyword "assert" and an image, while there are more than a million Jupyter notebooks available on GitHub. This suggests that the practice of assertion is still relatively uncommon.
We believe that this is due to a lack of knowledge among practitioners regarding testing approaches and the absence of adequate tooling to support the assertion of model properties. We delve into this issue further in Section~\ref{sec:fw}.

Additionally the results from RQ2, we see several examples of assertions that fail to capture all the information gained from its visual counter-part. Our observations indicate a need to bridge the gap between qualitative assessment of ML systems using visualisations and deriving analytical assertions from the visualisations. We find the need for automated tools that make this translation process easier for AI practitioners.
